---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
## MLM Exercise 1 ##
**Clemens Spielvogel**

Loading the milk dataset

```{r}
library(flexclust)
data(milk)
```

# Summarize the data. What is it about?
```{r}
summary(milk)
plot(milk)
```

# Use PCA to visualize the data in two dimensions.
```{r}
pr.out <- prcomp(milk, scale=T)
biplot(pr.out)
```

# What information is given on the four axes of the biplot? What
# do dolphins and seals have in common?
```{r}

```

# Cluster the milk data using hierarchical clustering. What kind of
# grouping do you see? What distance measure and linkage
# method did you use?
```{r}

```

# Plot a heatmap of the milk data. How would you modify the
# breaks in order to see differences in ash, lactose and protein?
```{r}

```

# Cluster the milk data using k–means clustering. How many
# clusters are in the data?
```{r}

```
# Visualize your cluster solution on the first and second principal
# component using the argument xlabs
```{r}

```
